Instruction

### 2019-01-13 script/Rmd/instruction.Rmd
Update instruction

---
title: "Instruction"
author: "Atsuko Tominaga"
date: "26/12/2018"
output:
  html_document:
    css: style.css
---

@@

<style type="text/css">
/* Whole document: */
body{
  font-family: Helvetica;
  font-size: 14pt;
}
</style>

## PARTICIPANT RECRUITMENT:
- More than 10 years experience to play the piano
- Basic English skills

## BEFORE PARTICIPANT ARRIVES:
- Devices
1. Connect the audio interface (Focusrite Scarlett 6i6) to Macbook Pro.
2. Connect twp headphones to the audio interface.
3. Connect the piano to the audio interface.
4. Turn on the piano, the audio interface and the screen in front of the piano.
5. Open “Focusrite Control” app ![](./image/focusriteControl.jpg){ width=5% } and click “Load from device”.

@@

1. Go to Desktop >> Atsuko >> expertpiano >> open the “mainPatch.maxpat” and the “imageDisplay.maxpat”.
2. Move the window of the “imageDisplay.maxpat” to the right (on the screen in front of the piano”) and press F for a fullscreen mode.
3. Read the instruction for the “mainPatch.maxpat" below.
    + Start a trial with the space key.
    + Stop a trial with the Z key.
    + The blue patcher is used to change an image of the screen and start a metronome manually (mainly used for a practice session and instructions).
    + The green patcher shows ongoing recordings.
    + The yellow patcher shows the name of the current file.
    + The pink patcher (hidden) reads the condition of the current participant.

![](./image/mainPatch_screen.png)

@@

### Introduction

*Thank you for participating in the experiment. The aim of the experiment is to investigate how people play a piece of music expressively. The experiment is going to last about one hour.*

*If you have any questions or concerns, please ask the experimenter at any time about the nature of the study or the methods we are using. Also, you have the right to withdraw from the experiment at any time.*

*Before we start the experiment, please read the informed consent form carefully and fill it out if you agree to take part in the study.*

@@

**[ Click “inst_g1” ]**

![](./image/inst_g1.png){ width=80% }

@@

![](./image/stim_n.png){ width=80% }

@@

*Please practise until you feel that you confortably perform the piece without pitch errors. After practice, we will have a brief test to make sure you can perform the piece. Also, you don't have to memorise the piece as you can see sheet music in front of you. Let me know when you are ready for the brief test.*

@@

**[ Click "inst_g2" ]**

![](./image/inst_g2.png){ width=80% }

@@

*You are now going to perform the piece in an expressive style indicated by the musical notation. I will show sheet music with the musical notation on the screen in front of you. Please read the notation and perform the piece 5 times according to the notation.*

**[ Click 1st Stimulus ]**
**[ Explain the musical notation]**

![](./image/stim_a.png){ width=80% }

@@

*Thank you. Do you have any questions?*

@@

*Thank you. Now, we are moving on to the different musical notation. Again, I will show sheet music with the musical notation on the screen in front of you. Please read the notation and perform the piece 5 times according to the notation.*

**[ Click 2nd Stimuli ]**
**[ Explain the musical notation]**

![](./image/stim_d.png){ width=80% }

@@

> 3rd Stimulus

*Thank you. Now, we are moving on to the different musical notation. Again, I will show sheet music with the musical notation on the screen in front of you. Please read the notation and perform the piece 5 times according to the notation.*

**[ Click 3rd Stimulus ]**
**[ Explain the musical notation]**

![](./image/stim_t.png){ width=80% }

@@

*Thank you. Do you have any questions?*

*Thank you. Next, you will perform the same piece again but in a different condition.*

*You are now going to perform the piece in an expressive style indicated by the musical notation. I will show sheet music with the musical notation on the screen in front of you. Please read the notation and perform the piece 5 times according to the notation.*

**[ Click 1st Stimulus ]**
**[ Explain the musical notation]**

*Thank you. Do you have any questions?*

@@

*Thank you. Now, we are moving on to the different musical notation. Again, I will show sheet music with the musical notation on the screen in front of you. Please read the notation and perform the piece 5 times according to the notation.*

@@

*Thank you. Do you have any questions?*

> 3rd Stimulus

*Thank you. Now, we are moving on to the different musical notation. Again, I will show sheet music with the musical notation on the screen in front of you. Please read the notation and perform the piece 5 times according to the notation.*

**[ Click 3rd Stimulus ]**
**[ Explain the musical notation]**

*Thank you. Do you have any questions?*

@@

*Thank you. This is the end of the experiment. Lastly, could you please fill in the questionnaire?*

@@

*Thank you for coming today and please feel free to contact me if you have any questions about my study.*

>>>>

---
title: "Instruction"
author: "Atsuko Tominaga"
date: "13/01/2019"
output:
  html_document:
    css: style.css
---

@@

<style type="text/css">
/* Whole document: */
body{
  font-family: Helvetica;
  font-size: 14pt;
}
span{
  color:red
}
</style>

## PARTICIPANT RECRUITMENT:

- More than 10 years experience to play the piano
- Basic English skills

## BEFORE PARTICIPANT ARRIVES:
- Devices
1. Connect the audio interface (Focusrite Scarlett 6i6) to Macbook Pro.
2. Connect two headphones to the audio interface.
3. Connect the piano to the audio interface.
4. Turn on the piano, the audio interface and the screen in front of the piano.
5. Open “Focusrite Control” app ![](./image/focusriteControl.jpg){ width=5% } and click “Load from device”.

@@

1. Go to Desktop >> Atsuko >> expertpiano >> open the “mainPatch.maxpat” and the “imageDisplay.maxpat”.
2. Move the window of the “imageDisplay.maxpat” to the right (on the screen in front of the piano”) and press F for a fullscreen mode.
3. Read the instruction for the “mainPatch.maxpat" below.
    + Start a trial with the A key.
    + Stop a trial with the D key.
    + If you want to record the same trial again, use the reset button.

@@

### Introduction
<span>
*Thank you for participating in the experiment. The aim of the experiment is to investigate how people play a piece of music expressively. The experiment is going to last about one hour.*<br>
*If you have any questions or concerns, please ask the experimenter at any time about the nature of the study or the methods we are using. Also, you have the right to withdraw from the experiment at any time.*<br>
*Before we start the experiment, please read the informed consent form carefully and fill it out if you agree to take part in the study.*
</span>

@@

**[ Click “inst_1” ]**

![](./image/inst_1.png){ width=80% }

@@

![](./image/prac_stim_n.png){ width=80% }

@@

<span>
*Please practise until you feel that you confortably perform the piece without pitch errors. After practice, we will have a brief test to make sure you can perform the piece. Also, you don't have to memorise the piece as you can see sheet music in front of you. Let me know when you are ready for the brief test.*
</span>

@@

**[ Click "inst_2" ]**

![](./image/inst_2.png){ width=80% }

@@

<span>
*You are now going to perform the piece in an expressive style indicated by the musical notation. I will show sheet music with the musical notation on the screen in front of you. Please read the notation and if you have any question, please ask me now (Also explain the main information of the expression). If you don't have any question, I will give you the sound of the metronome and please perform the piece according to the notation.*
</span>

**[ Open practicePatch ]**

**[ Click 1st Stimulus ]**

![](./image/prac_stim_a.png){ width=80% }

@@

<span>
*Thank you. Do you have any questions?*
</span>

@@

<span>
*Thank you. Now, we are moving on to the different musical notation. Again, I will show sheet music with the musical notation on the screen in front of you. Please read the notation and perform the piece 5 times according to the notation.*
</span>

**[ Click 2nd Stimuli ]**

![](./image/prac_stim_d.png){ width=80% }

@@

<span>
*Thank you. Next, you will perform the same piece again but in a different condition.*
</span>

<span>
*You are now going to perform the piece in an expressive style indicated by the musical notation. I will show sheet music with the musical notation on the screen in front of you. Please read the notation and perform the piece 5 times according to the notation.*
</span>

**[ Click 1st Stimulus ]**

@@

<span>
*Thank you. Do you have any questions?*
</span>

@@

<span>
*Thank you. Now, we are moving on to the different musical notation. Again, I will show sheet music with the musical notation on the screen in front of you. Please read the notation and perform the piece 5 times according to the notation.*
</span>

@@

<span>
*Thank you. Do you have any questions?*
</span>

@@

<span>
*Thank you. This is the end of the experiment. Lastly, could you please fill in the questionnaire?*
</span>

@@

<span>
*Thank you for coming today and please feel free to contact me if you have any questions about my study.*
</span>
